Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-19 cordillera-cycle.tex
Update author list.

% Authors
\Author[1,2]{J.}{Seguinot}
\Author[3]{M.}{Margold}
\Author[2]{I.}{Rogozhina}
\Author[1]{A.~P.}{Stroeven}
\runningauthor{J.~Seguinot et~al.}
\correspondence{J.~Seguinot (julien.seguinot@natgeo.su.se)}

@@

Once more, snapshots of modelled deglacial ice sheet configurations
(Figs.~\ref{fig:deglacshots-grip} and~\ref{fig:deglacshots-epica}%
\footnote{I produced one figure for each run, but as you could expect from
    Fig.~\ref{fig:deglac}, Figs.~\ref{fig:deglacshots-grip}
    and~\ref{fig:deglacshots-epica} look very similar. One of them would
    probably be enough, or?}) provide a
poor medium for direct comparison with geomorphological evidence of the ice
retreat. Here, we compute a map of deglacial, basal flow directions immediately
preceding exposure of ice-free land or cessation of sliding upon the approach
of the retreating margin (Fig.~\ref{fig:lastflow}). On the northern and
southern front of the ice sheet and in the Liard Lowland, the resulting map
show similarities with patterns of glacial lineations
(\citealp{Prest.etal.1968}; \citealp[Fig.~1.12]{Clague.1989};
\citealp[Fig.~2]{Kleman.etal.2010}; \citealp[Fig.~2]{Margold.etal.2013}).
However, such is not the case on the Interior Plateau of British Columbia,
where both simulations predicts neglictible basal sliding during deglaciation
(Fig.~\ref{fig:lastflow}), whereas glacial lineation maps indicate substantial
eastward flow.

>>>>

% Authors
\Author[1,2]{J.}{Seguinot}
\Author[3]{M.}{Margold}
\Author[2]{I.}{Rogozhina}
\Author[1]{A.~P.}{Stroeven}
\Author[1]{J.}{Kleman}
\runningauthor{J.~Seguinot et~al.}
\correspondence{J.~Seguinot (julien.seguinot@natgeo.su.se)}

@@

Once more, snapshots of modelled deglacial ice sheet configurations
(Figs.~\ref{fig:deglacshots-grip} and~\ref{fig:deglacshots-epica}%
\footnote{I produced one figure for each run, but as you could expect from
    Fig.~\ref{fig:deglac}, Figs.~\ref{fig:deglacshots-grip}
    and~\ref{fig:deglacshots-epica} look very similar. One of them would
    probably be enough, or?}) provide a
poor medium for direct comparison with geomorphological evidence of the ice
retreat. Here, we compute a map of deglacial, basal flow directions immediately
preceding exposure of ice-free land or cessation of sliding upon the approach
of the retreating margin (Fig.~\ref{fig:lastflow}). On the northern and
southern front of the ice sheet and in the Liard Lowland, the resulting map
show similarities with patterns of glacial lineations
(\citealp{Prest.etal.1968}; \citealp[Fig.~1.12]{Clague.1989};
\citealp[Fig.~2]{Kleman.etal.2010}; \citealp[Fig.~2]{Margold.etal.2013}).
However, such is not the case on the Interior Plateau of British Columbia,
where both simulations predicts negligible basal sliding during deglaciation
(Fig.~\ref{fig:lastflow}), whereas glacial lineation maps indicate substantial
eastward flow.
